
Although \wjets and QCD multijet processes (figure~\ref{}) do not contain two
leptons in the final state, they are expected to contribute in the
signal region in cases where a jet is mis-reconstructed as a prompt
lepton.  Such leptons are considered ``fake'', whether they are
mis-reconstructed from charged hadron tracks or from heavy hadron
decays to true non-prompt leptons. Given that this background is due
to instrumental effects, a reliable estimate can only be obtained with
data-driven methods. In contrast to the data-driven estimates
described above, the procedure described in the following section
is purely data-driven in the sense that both the normalization and the
kinematic shapes are derived from a control region. In other words,
\wjets and multijet MC templates are not used at all.

The \wjets CR is the same as the analysis signal region except that
the object selection has been adjusted to enrich the region with fake
leptons. This is accomplished by loosening the quality criteria for
one of the leptons and requiring that it does not pass the analysis-level
lepton selection, while the other lepton is required to pass. The
former lepton type is referred to as ``anti-identified''. For
anti-identified electrons, the calorimeter isolation requirement is
loosened to $\et^{R=0.3}/\et<0.30$, the track isolation requirement
is $p_T^{R=0.3}/\et<0.16$, the conversion flag and $b$-layer
requirements are removed and the electron is required to fail the {\it
  medium} identification requirement. For muons, the calorimeter
isolation requirements are also loosened, the track isolation
requirements are completely removed, and the transverse impact parameter
significance cut is removed.

To extrapolate from the \wjets CR to the SR, first the non-\wjets
background is subtracted, and then an extrapolation factor, called the
fake factor, is applied. The fake factor is defined as

\begin{equation}
\label{chap:analysis:equation:fake_factor}
f_{\textrm{fake}} =
\frac{N_{\textrm{id}}}{N_{\textrm{anti-id}}}
\end{equation}

\noindent
where $N_{\textrm{id}}$ is the number of jets that pass the
full lepton selection and $N_{\textrm{anti-id}}$ is the number
of jets which pass the anti-identified selection. \fakefact is
evaluated with jets in a jet-rich $Z$ CR in bins of lepton \pt~and
$\eta$. From the fake factor, the \wjets estimate in the SR is given
by

\begin{equation}
\label{chap:analysis:equation:wjets_est}
N_{id+id}^{\wjets} = \fakefact\cdot (N_{\textrm{id+anti-id}} -
N_{\textrm{id+anti-id}}^{\textrm{QCD}} -
N_{\textrm{id+anti-id}}^{\textrm{non-fake,MC}})
\end{equation}

\noindent
where $N_{\textrm{id+anti-id}}$ is the total number of events in the
\wjets CR, $N_{\textrm{id+anti-id}}^{\textrm{QCD}}$ is data-driven QCD
multijet estimate in the \wjets CR, which is described below, and
$N_{\textrm{id+anti-id}}^{\textrm{non-fake,MC}}$ is the MC prediction
for the non-fake contribution in the \wjets CR. 

The dijet control region is similar to the \wjets control region,
except that instead of the requirement of one anti-identified lepton,
both of the leptons satisfy this requirement. The fake factors for
this background are obtained using the same procedure as \wjets,
but in a region that is rich in QCD multi-jets. Because there
are two fake leptons, two fake factors are derived, where the second
fake factor accounts for bias introduced with the requirement of an
additional anti-identified lepton. The QCD estimate in the signal
region is then expressed as

\begin{equation}
N_{id+id}^{\textrm{QCD}} = \fakefact^{\prime\prime}\cdot\fakefact^{\prime}\cdot (N_{\textrm{anti-id+anti-id}} -
N_{\textrm{anti-id+anti-id}}^{\wjets\textrm{,MC}} -
N_{\textrm{anti-id+anti-id}}^{\textrm{non-fake,MC}})
\end{equation}

\noindent
where $\fakefact^{\prime\prime}$ and $\fakefact^{\prime}$ are the two
dijet fake factors, $N_{\textrm{anti-id+anti-id}}$ is the total number
of data events in the dijet CR,
$N_{\textrm{anti-id+anti-id}}^{\wjets\textrm{,MC}}$ is the \wjets
contamination predicted by simulation in the CR, and
$N_{\textrm{anti-id+anti-id}}^{\textrm{non-fake,MC}}$ is the non-fake
contamination. 

To estimate the QCD contamination in the \wjets CR
($N_{\textrm{id+anti-id}}^{\textrm{QCD}}$ in
equation~\ref{chap:analysis:equation:wjets_est}), there is an
extrapolation from the dijet CR to the \wjets CR, given by

\begin{equation}
N_{id+anti-id}^{\textrm{QCD}} = 2\cdot\fakefact^{\prime\prime}\cdot (N_{\textrm{anti-id+anti-id}} -
N_{\textrm{anti-id+anti-id}}^{\wjets\textrm{,MC}} -
N_{\textrm{anti-id+anti-id}}^{\textrm{non-fake,MC}})
\end{equation}

\noindent
where the factor of two arises due to the fact that events with two
anti-identified leptons can enter the \wjets CR if either lepton is
identified. 

The uncertainties associated with this data-driven estimate are
relatively large. As mentioned above, the \wjets fake factor is obtained from a
$Z$ control region. In order to account for kinematic differences
between jets in the $Z$ control region and those associated
with \wjets, fake factors from simulated $W$ and $Z$ samples are
compared, and the resulting difference is used to correct the
$Z$-derived fake factor from data, and also assigned as a
systematic. For electron (muon) fakes, the uncertainty is 20\%
(22\%). In addition, the dependence of the fake factor on the
electroweak contamination in the $Z$ control region is evaluated by
computing the factor with and without these processes subtracted,
yielding uncertainties in the range 11\%-25\% (3\%-21\%) for electron
(muon) fakes. Finally, the statistical uncertainty from the control
region data is considered. For electron (muon) fakes, this
uncertainty falls in the range 18\%-52\% (10\%-34\%). Uncertainties
associated with the fake factor from the di-jet CR are evaluated
similarly, and shown to be dominated by the uncertainty due to the CR
sample choice of 60\% (40\%) for electron (muon) fakes.  

Backgrounds due to fakes are relatively small in the BDT signal
region. The primary reason for this is that the cross sections of
these processes are small in the two jet bin relative to the other jet
bins for which the above estimation technique has been
developed. Moreover, jets from \wjets and QCD multijet
processes tend to be more central in rapidity, and because the BDT
selects forward jets, these processes are kinematically
suppressed. The \wjets estimate in the
\emme channel relative to the total background prediction is 2\%, 3\%,
and 0\%, in the respective BDT fit bins and the QCD estimate is even
smaller-- 0.4\%, 0\%, and 0\%. 


